Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-25 sections/eval.tex
Update on Overleaf.

\begin{align*}
    \finchplan(queries..., names...) \quad\quad\quad \finchquery(name, expr) \quad\quad\quad \finchreorder(expr, idxs...)\\
    \finchrelabel(expr, idxs...) \quad\quad\quad \finchmapjoin(op, exprs...) \quad\quad\quad \finchaggregate(op, expr)\\
    \finchtable(tns, idxs...)  \quad\quad\quad\quad\quad \finchalias(name) \quad\quad\\
     expr:= \finchreorder | \finchrelabel |\finchmapjoin | \finchaggregate | \finchtable | \finchalias\quad\quad
\end{align*}

Given this language, we now describe how to define a few example functions from the API as Finch Logic expressions, 
\begin{align*}
\text{sum(M, dims=[2])} &\rightarrow \finchplan(\finchquery(out,\finchaggregate(\finchrelabel(M, i_1,\ldots,i_d), i_2)), out)\\
\text{matmul(A, B)} &\rightarrow \finchplan(\finchquery(out,\finchaggregate(\finchmapjoin(*, \finchrelabel(A, i, j), \finchrelabel(B, j, k)), j)), out)\\
\end{align*}

>>>>

\begin{align*}
    \finchplan(queries..., names...) \quad\quad\quad \finchquery(name, expr) \quad\quad\quad \finchreorder(expr, idxs...)\\
    \finchrelabel(expr, idxs...) \quad\quad\quad \finchmapjoin(op, exprs...) \quad\quad\quad \\
    \finchaggregate(op, expr)\quad\quad\quad \finchtable(tns, idxs...)  \quad\quad\quad\quad\quad \finchalias(name) \quad\quad\\
     expr:= \finchreorder | \finchrelabel |\finchmapjoin | \finchaggregate | \finchtable | \finchalias\quad\quad
\end{align*}

Given this language, we now describe how to define a few example functions from the API as plans in the Finch Logic language,
\begin{align*}
\text{sum(M, dims=[2])} &\rightarrow \finchplan(\finchquery(out,\finchaggregate(\finchrelabel(M, i_1,\ldots,i_d), i_2)), out)\\
\text{matmul(A, B)} &\rightarrow \finchplan(\finchquery(out,\finchaggregate(\finchmapjoin(*, \finchrelabel(A, i, j), \finchrelabel(B, j, k)), j)), out)\\
\end{align*}
Notably, these plans do not specify
